Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-08 Paper.tex
Changed Div &c. to allow doc/0.

With ubiquitous internet connections in most places of the world, global information transmission has become incredibly cheap. Technological-rooted movements like Bitcoin have demonstrated through the power of the default, consensus mechanisms and voluntary respect of the social contract that it is possible to use the internet to make a decentralised value-transfer system, shared across the world and virtually free to use. This system can be said to be a very specialised version of a cryptographically secure, transaction-based state machine. Follow-up systems such as namecoin adapted this original ``currency application'' of the technology into other applications allbeit rather simplistic ones.

@@

The machine can have exceptional execution for several reasons, including stack underflows, invalid instructions and divides by zero. These unambiguously and validly result in immediate halting of the machine with all state changes left intact. The one piece of exceptional execution that does not leave state changes intact is the out-of-gas (OOG) exception. Here, the machine halts immediately and reports the issue to the execution agent (either the transaction processor or, recursively, the spawning execution environment) and which will deal with it separately.

@@

This states that the execution is in an exceptional halting state if there is insufficient gas or if there are insufficient stack items. The astute read will realise that this implies that no instruction can, through its execution, cause an exceptional halt.

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{0s: Stop and Arithmetic Operations}} \\
\multicolumn{5}{l}{All arithmetic is modulo $2^{256}$.} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x00 & {\small STOP} & 0 & 0 & Halts execution. \\
&&&& $\mathbb{M}'_R = []$ \\
\midrule
0x01 & {\small ADD} & 2 & 1 & Addition operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] + \mathbb{M}_S[1]$ \\
\midrule
0x02 & {\small MUL} & 2 & 1 & Multiplication operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] \times \mathbb{M}_S[1]$ \\
\midrule
0x03 & {\small SUB} & 2 & 1 & Subtraction operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] - \mathbb{M}_S[1]$ \\
\midrule
0x04 & {\small DIV} & 2 & 1 & Integer division operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \lfloor\mathbb{M}_S[0] \div \mathbb{M}_S[1]\rfloor$ \\
\midrule
0x05 & {\small SDIV} & 2 & 1 & Signed integer division operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \lfloor\mathbb{M}_S[0] \div \mathbb{M}_S[1]\rfloor$ \\
&&&& Where all values are treated as signed 256-bit integers for the purposes of this operation. \\
\midrule
0x06 & {\small MOD} & 2 & 1 & Modulo remainder operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] \mod{ \mathbb{M}_S[1] }$ \\
\midrule
0x07 & {\small SMOD} & 2 & 1 & Modulo remainder operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] \mod{ \mathbb{M}_S[1] }$ \\
&&&& Where all values are treated as signed 256-bit integers for the purposes of this operation. \\
\midrule
0x08 & {\small EXP} & 2 & 1 & Exponential operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] ^ {\mathbb{M}_S[1] }$ \\
\midrule
0x09 & {\small NEG} & 1 & 1 & Negation operation. \\
&&&& $\mathbb{M}'_T[0] \equiv -\mathbb{M}_S[0]$ \\
&&&& Where all values are treated as signed 256-bit integers for the purposes of this operation. \\
\midrule
0x0a & {\small LT} & 2 & 1 & Less-than comparision. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] < \mathbb{M}_S[1] \\ 0 & \text{otherwise} \end{cases}$ \\
\midrule
0x0b & {\small GT} & 2 & 1 & Greater-than comparision. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] > \mathbb{M}_S[1] \\ 0 & \text{otherwise} \end{cases}$ \\
\midrule
0x0c & {\small EQ} & 2 & 1 & Equality comparision. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] = \mathbb{M}_S[1] \\ 0 & \text{otherwise} \end{cases}$ \\
\midrule
0x0d & {\small NOT} & 1 & 1 & Simple not operator. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] = 0 \\ 0 & \text{otherwise} \end{cases}$ \\
\end{tabular*}

>>>>

With ubiquitous internet connections in most places of the world, global information transmission has become incredibly cheap. Technological-rooted movements like Bitcoin have demonstrated through the power of the default, consensus mechanisms and voluntary respect of the social contract that it is possible to use the internet to make a decentralised value-transfer system, shared across the world and virtually free to use. This system can be said to be a very specialised version of a cryptographically secure, transaction-based state machine. Follow-up systems such as Namecoin adapted this original ``currency application'' of the technology into other applications allbeit rather simplistic ones.

@@

The machine can have exceptional execution for several reasons, including stack underflows and invalid instructions. These unambiguously and validly result in immediate halting of the machine with all state changes left intact. The one piece of exceptional execution that does not leave state changes intact is the out-of-gas (OOG) exception. Here, the machine halts immediately and reports the issue to the execution agent (either the transaction processor or, recursively, the spawning execution environment) and which will deal with it separately.

@@

This states that the execution is in an exceptional halting state if there is insufficient gas or if there are insufficient stack items. The astute reader will realise that this implies that no instruction can, through its execution, cause an exceptional halt.

@@

\begin{tabular*}{\columnwidth}[h]{rlrrl}
\toprule
\multicolumn{5}{c}{\textbf{0s: Stop and Arithmetic Operations}} \\
\multicolumn{5}{l}{All arithmetic is modulo $2^{256}$.} \vspace{5pt} \\
\textbf{Value} & \textbf{Mnemonic} & $\delta$ & $\alpha$ & \textbf{Description} \vspace{5pt} \\
0x00 & {\small STOP} & 0 & 0 & Halts execution. \\
&&&& $\mathbb{M}'_R = []$ \\
\midrule
0x01 & {\small ADD} & 2 & 1 & Addition operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] + \mathbb{M}_S[1]$ \\
\midrule
0x02 & {\small MUL} & 2 & 1 & Multiplication operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] \times \mathbb{M}_S[1]$ \\
\midrule
0x03 & {\small SUB} & 2 & 1 & Subtraction operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] - \mathbb{M}_S[1]$ \\
\midrule
0x04 & {\small DIV} & 2 & 1 & Integer division operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases}0 & \text{if} \quad \mathbb{M}_S[1] = 0\\ \lfloor\mathbb{M}_S[0] \div \mathbb{M}_S[1]\rfloor & \text{otherwise}\end{cases}$  \\
\midrule
0x05 & {\small SDIV} & 2 & 1 & Signed integer division operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases}0 & \text{if} \quad \mathbb{M}_S[1] = 0\\ \lfloor\mathbb{M}_S[0] \div \mathbb{M}_S[1]\rfloor & \text{otherwise}\end{cases}$  \\
&&&& Where all values are treated as signed 256-bit integers for the purposes of this operation. \\
\midrule
0x06 & {\small MOD} & 2 & 1 & Modulo remainder operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases}0 & \text{if} \quad \mathbb{M}_S[1] = 0\\ \mathbb{M}_S[0] \bmod \mathbb{M}_S[1] & \text{otherwise}\end{cases}$  \\
\midrule
0x07 & {\small SMOD} & 2 & 1 & Modulo remainder operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases}0 & \text{if} \quad \mathbb{M}_S[1] = 0\\ \mathbb{M}_S[0] \bmod \mathbb{M}_S[1] & \text{otherwise}\end{cases}$  \\
&&&& Where all values are treated as signed 256-bit integers for the purposes of this operation. \\
\midrule
0x08 & {\small EXP} & 2 & 1 & Exponential operation. \\
&&&& $\mathbb{M}'_T[0] \equiv \mathbb{M}_S[0] ^ {\mathbb{M}_S[1] }$ \\
\midrule
0x09 & {\small NEG} & 1 & 1 & Negation operation. \\
&&&& $\mathbb{M}'_T[0] \equiv -\mathbb{M}_S[0]$ \\
&&&& Where all values are treated as signed 256-bit integers for the purposes of this operation. \\
\midrule
0x0a & {\small LT} & 2 & 1 & Less-than comparision. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] < \mathbb{M}_S[1] \\ 0 & \text{otherwise} \end{cases}$ \\
\midrule
0x0b & {\small GT} & 2 & 1 & Greater-than comparision. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] > \mathbb{M}_S[1] \\ 0 & \text{otherwise} \end{cases}$ \\
\midrule
0x0c & {\small EQ} & 2 & 1 & Equality comparision. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] = \mathbb{M}_S[1] \\ 0 & \text{otherwise} \end{cases}$ \\
\midrule
0x0d & {\small NOT} & 1 & 1 & Simple not operator. \\
&&&& $\mathbb{M}'_T[0] \equiv \begin{cases} 1 & \text{if} \quad \mathbb{M}_S[0] = 0 \\ 0 & \text{otherwise} \end{cases}$ \\
\end{tabular*}
